---
title: "Individual Data Summary, Markdown 2"
author: "Julie Norman"
date: "11/17/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. create new df: individual
```{r}
library(tidyverse)
library(haven)
#full_df = read_dta("~/Documents/Economics/Econometrics Project/CEEPASurvey.dta")

full_df = read_csv("df2")
ind = read_csv("df2")
```


2. dplyr select to get rid of all other 
  "starts with"
  check the column grab 7*39 (household code)


```{r}
ind <- ind %>% 
  select(starts_with("hhcode"),
         starts_with("gender"), 
         starts_with("age"), 
         starts_with("married"), 
         starts_with("educ"), 
         starts_with("farmwork"), 
         starts_with("nfarmwork")) 
                        
```

4. create new df "individual1"
3. Do 39x  
  dplyr selector "contains(k)" grab six columns that have "k" individaul number in them dplyr in loop 
  grab household code also
  rename columns "age", "gender" accross all 39 
  

```{r}
df_list <- rep(list(NA), 38) 

for(k in 1:38){
  regex_ind <- paste0("[a-z]+",k,"\\b")
  genderk <- paste0("gender", k)
  agek <- paste0("age", k)
  marriedk <- paste0("married", k)
  educk <- paste0("educ", k)
  farmworkk <- paste0("farmwork", k)
  nfarmworkk <- paste0("nfarmwork", k)
  
  indk <- ind %>% 
    select(hhcode, matches(regex_ind)) %>% 
    rename_(gender = genderk, 
            age = agek,
            married = marriedk,
            educ = educk,
            farmwork = farmworkk,
            nfarmwork = nfarmworkk)
  df_list[[k]] <- indk
  }


```

5. Rbind data frames  

```{r}
ind_long <- do.call(rbind, df_list)


```

5.5 deleting with complete na

```{r}
ind_long <- ind_long[rowSums(is.na(ind_long)) < 6, ]
```

6. group by household code, gender 
7. summarize by mean of each, count for proportions 


```{r}
hhg_summary <- ind_long %>% 
  group_by(hhcode, gender) %>%
  summarize(hhg_count = n(), 
            educ_mean = mean(educ),
            educ_med = median(educ),
            farmwork_countN = sum(farmwork == "no"),
            farmwork_countY = sum(farmwork == "yes"), 
            nfarmwork_countN = sum(nfarmwork == "no"),
            nfarmwork_countY = sum(nfarmwork == "yes"))

head(hhg_summary)
```

8. seperate females and males


```{r}
hhg_summary <- melt(hhg_summary, id.vars = c("hhcode", "gender"))
hh_summary <- dcast(hhg_summary, hhcode ~ variable + gender)

head(hh_summary)
```

10. specify male and female education colums 
9. 1 row per household, join to the original data 

inner_join df1, df2 by = hhcode 
```{r}
gjoin_df <- inner_join(hh_summary, full_df, by = "hhcode")

head(gjoin_df)
```



# Write CSV

```{r}
write.csv(gjoin_df, "df3")
```







